Simulation Study: Varying Null Proportion

### 2018-06-09 datasets/simulations/simulations-varyingpi0-lowsignal.Rmd
Add more levels for varying pi0 simulations

---
title: "Simulation Study: Varying Null Proportion (lower signal)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with varying proportion of null tests. An informative covariate is included
in the setting as described in `simulations-informative-sine.Rmd`.

@@

## intermediary files we create below
null05_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop05.rds")
null10_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop10.rds")
null20_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop20.rds")
null50_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop50.rds")
null80_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop80.rds")
null90_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop90.rds")
null95_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop95.rds")
null99_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop99.rds")

@@

@@

>>>>

---
title: "Simulation Study: Varying Null Proportion"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with varying proportion of null tests. An informative covariate is included
in the setting as described in `simulations-informative-sine.Rmd`.
The simulations are identical to those performed in `simulations-varyingpi0.Rmd`
except that the strength of the "singal" (the effect size for non-null tests)
is weaker (smaller).

@@

## intermediary files we create below
null05_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop05.rds")
null10_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop10.rds")
null20_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop20.rds")
null30_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop30.rds")
null40_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop40.rds")
null50_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop50.rds")
null60_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop60.rds")
null70_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop70.rds")
null80_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop80.rds")
null90_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop90.rds")
null95_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop95.rds")
null99_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop99.rds")

@@

# 30% Null Setting

Next, we consider the setting where 30% of tests are null.

```{r null30-parameters}
pi0 <- pi0_sine(0.30)             # numeric: proportion of null hypotheses
seed <- 511
```

```{r null30-run-simulation}
if (file.exists(null30_file)) {
    res <- readRDS(null30_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null30_file)
}
```

```{r null30-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

```{r, null30-diag-scatter, results = "hide", fig.width=4.5, fig.height=3.5}
rank_scatter(onerun, pvalue = "pval", covariate = "ind_covariate")
```

```{r, null30-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

```{r null30-metrics-averages, results = "hide"}
resdf <- plotsim_standardize(res, alpha = seq(0.01, 0.10, 0.01))

```{r null30-metrics-covlineplot, results = "hide"}
covariateLinePlot(res, alpha = ualpha, covname = "effect_size")

```{r null30-metrics-upset, results = "hide"}
if (numberMethodsReject(resdf, alphacutoff = ualpha, filterSet = excludeSet) >= 3) {
    aggupset(res, alpha = ualpha, supplementary = FALSE, return_list = FALSE)
} else {
    message("Not enough methods found rejections at alpha ", ualpha, 
            "; skipping upset plot")
}
```

# 40% Null Setting

Next, we consider the setting where 40% of tests are null.

```{r null40-parameters}
pi0 <- pi0_sine(0.40)             # numeric: proportion of null hypotheses
seed <- 515
```

```{r null40-run-simulation}
if (file.exists(null40_file)) {
    res <- readRDS(null40_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null40_file)
}
```

```{r null40-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

```{r, null40-diag-scatter, results = "hide", fig.width=4.5, fig.height=3.5}
rank_scatter(onerun, pvalue = "pval", covariate = "ind_covariate")
```

```{r, null40-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

```{r null40-metrics-averages, results = "hide"}
resdf <- plotsim_standardize(res, alpha = seq(0.01, 0.10, 0.01))

```{r null40-metrics-covlineplot, results = "hide"}
covariateLinePlot(res, alpha = ualpha, covname = "effect_size")

```{r null40-metrics-upset, results = "hide"}
if (numberMethodsReject(resdf, alphacutoff = ualpha, filterSet = excludeSet) >= 3) {
    aggupset(res, alpha = ualpha, supplementary = FALSE, return_list = FALSE)
} else {
    message("Not enough methods found rejections at alpha ", ualpha, 
            "; skipping upset plot")
}
```

@@

# 60% Null Setting

Next, we consider the setting where 60% of tests are null.

```{r null60-parameters}
pi0 <- pi0_sine(0.60)             # numeric: proportion of null hypotheses
seed <- 1502
```

```{r null60-run-simulation}
if (file.exists(null60_file)) {
    res <- readRDS(null60_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null60_file)
}
```

```{r null60-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

```{r, null60-diag-scatter, results = "hide", fig.width=4.5, fig.height=3.5}
rank_scatter(onerun, pvalue = "pval", covariate = "ind_covariate")
```

```{r, null60-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

```{r null60-metrics-averages, results = "hide"}
resdf <- plotsim_standardize(res, alpha = seq(0.01, 0.10, 0.01))

```{r null60-metrics-covlineplot, results = "hide"}
covariateLinePlot(res, alpha = ualpha, covname = "effect_size")

```{r null60-metrics-upset, results = "hide"}
if (numberMethodsReject(resdf, alphacutoff = ualpha, filterSet = excludeSet) >= 3) {
    aggupset(res, alpha = ualpha, supplementary = FALSE, return_list = FALSE)
} else {
    message("Not enough methods found rejections at alpha ", ualpha, 
            "; skipping upset plot")
}
```

# 70% Null Setting

Next, we consider the setting where 70% of tests are null.

```{r null70-parameters}
pi0 <- pi0_sine(0.70)             # numeric: proportion of null hypotheses
seed <- 1722
```

```{r null70-run-simulation}
if (file.exists(null70_file)) {
    res <- readRDS(null70_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null70_file)
}
```

```{r null70-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

```{r, null70-diag-scatter, results = "hide", fig.width=4.5, fig.height=3.5}
rank_scatter(onerun, pvalue = "pval", covariate = "ind_covariate")
```

```{r, null70-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

```{r null70-metrics-averages, results = "hide"}
resdf <- plotsim_standardize(res, alpha = seq(0.01, 0.10, 0.01))

```{r null70-metrics-covlineplot, results = "hide"}
covariateLinePlot(res, alpha = ualpha, covname = "effect_size")

```{r null70-metrics-upset, results = "hide"}
if (numberMethodsReject(resdf, alphacutoff = ualpha, filterSet = excludeSet) >= 3) {
    aggupset(res, alpha = ualpha, supplementary = FALSE, return_list = FALSE)
} else {
    message("Not enough methods found rejections at alpha ", ualpha, 
            "; skipping upset plot")
}
```

### 2018-06-09 datasets/simulations/simulations-varyingpi0.Rmd
Add more levels for varying pi0 simulations

## intermediary files we create below
null05_file <- file.path(resdir, "varyingpi0-benchmark-nullprop05.rds")
null10_file <- file.path(resdir, "varyingpi0-benchmark-nullprop10.rds")
null20_file <- file.path(resdir, "varyingpi0-benchmark-nullprop20.rds")
null50_file <- file.path(resdir, "varyingpi0-benchmark-nullprop50.rds")
null80_file <- file.path(resdir, "varyingpi0-benchmark-nullprop80.rds")
null90_file <- file.path(resdir, "varyingpi0-benchmark-nullprop90.rds")
null95_file <- file.path(resdir, "varyingpi0-benchmark-nullprop95.rds")
null99_file <- file.path(resdir, "varyingpi0-benchmark-nullprop99.rds")

>>>>

## intermediary files we create below
null05_file <- file.path(resdir, "varyingpi0-benchmark-nullprop05.rds")
null10_file <- file.path(resdir, "varyingpi0-benchmark-nullprop10.rds")
null20_file <- file.path(resdir, "varyingpi0-benchmark-nullprop20.rds")
null30_file <- file.path(resdir, "varyingpi0-benchmark-nullprop30.rds")
null40_file <- file.path(resdir, "varyingpi0-benchmark-nullprop40.rds")
null50_file <- file.path(resdir, "varyingpi0-benchmark-nullprop50.rds")
null60_file <- file.path(resdir, "varyingpi0-benchmark-nullprop60.rds")
null70_file <- file.path(resdir, "varyingpi0-benchmark-nullprop70.rds")
null80_file <- file.path(resdir, "varyingpi0-benchmark-nullprop80.rds")
null90_file <- file.path(resdir, "varyingpi0-benchmark-nullprop90.rds")
null95_file <- file.path(resdir, "varyingpi0-benchmark-nullprop95.rds")
null99_file <- file.path(resdir, "varyingpi0-benchmark-nullprop99.rds")
